Using traffic analysis to identify The Second Generation Onion Router

### 2010-12-31 thesis/thesis.tex
Include experiment in thesis file.

\chapter{Materials and Methods}

\section{Equipment Requirements}

The following list describes computer systems and hardware required to run the
data capture simulations:

\begin{itemize*}
  \item 1 Computer system running web browser and Tor
  \item 1 Computer running packet sniffing software
  \item N Computer systems running Tor, configured as bridges
  \item 1 Computer running web server and Tor directory server
  \item Cat 5 cable to connect all computer systems
  \item Network Hub or Switch capable of disabling ‘learning’
    \parencite{website:hub-reference}
\end{itemize*}

The computer systems running Tor bridges represent the simulation network.
Although it is feasible to have a single system representing the simulation
network the combined system load may be too great and introduce  excessive
latency.

Packet capture is a performance intensive application, one machine should be
reserved for this application. It must include adequate disk space, preferably
of a high speed.

The required software includes:

\begin{itemize*}
  \item Virtualisation software
  \item Web browser
  \item Tor
  \item Packet capture software
\end{itemize*}

\section{Procedure}

\subsection{Phase 1}

\subsubsection{Hardware Configuration}

All systems will be configured and connected to the same isolated network
through the hub as shown in Figure \ref{physical-setup}.

\begin{figure}[H]
  \centering\includegraphics[scale=0.6]{physical-setup}
  \caption{Physical Setup}
  \label{physical-setup}
\end{figure}

\subsubsection{Software Configuration}

Software is installed and configured on all machines. The simulation network is
configured to use the private Tor directory server rather than the public ones
specified by default \parencite{website:private-tor-network}.

The packet sniffer is configured to capture only the packets relevant for each
data set.

Figure \ref{network-diagram} shows the placement of applications and relevant
data flows.

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{network-diagram}
  \caption{Network Diagram}
  \label{network-diagram}
\end{figure}

\subsubsection{Simulations}

To provide a large training set, capture traffic can be generated by a series
of automated simulations. This stage of the research will include identifying a
number of commonly used websites and other hosts that employ TLS encryption,
and simulating these on the test network through mirroring or other means. This
will include selection of tools to assist in automating this process.

\subsubsection{Data Capture}

Three sets of data must be collected, and kept separate. The first set is a
sample that is known to belong to the anonymous networks in question. To
capture this the software will be configured to communicate using known
parameters. It will also be ensured that no other applications are
communicating using these parameters that may pollute the data set.

This first set of data can be partitioned to make the second set, which will be
used to confirm the false negative rate of the matching technique.

The third set of data must constitute traffic that is known to not contain any
traffic from the networks being catalogued. This data set will be used to
confirm the rate of false positives.

\subsection{Phase 2}

\subsubsection{Data Preparation}

The captured data will be in the data file format used by the capture software.
For analysis the most relevant information needs to be retrieved from the data
files and prepared in a suitable format for the matching algorithm. This stage
of the research includes identifying the attributes of the captured data that
would be most suitable for analytical purposes, and providing them in a format
suitable for processing by an automatic classifier.

\subsubsection{Analysis}

The training data set will be supplied to the algorithm for training purposes.
Once training is complete, this algorithm can be tested against the
confirmation data set to obtain the rate of false negatives. The regular
traffic will be used to determine the false positive rate. This allows the
construction of the Receiver Operating Characteristic (ROC) curve, a
measurement of the performance of the matching algorithm.

\section{Limitations}

The process has been designed with the goal of minimising variables that may
affect matching performance. This is unusual for traffic analysis papers which
typically sample real world traffic in large volumes. In the case of a machine
learning technique, this may bias the chosen algorithm against real world data,
making it impractical for any real world use.

\section{Schedule}

\begin{tabular}{llr}
  \toprule
  Activity & Duration & Date \\
  \midrule
  Phase 1 \\
  1 - Design simulations & 4 weeks \\
  2 - Setup test network & 1 week \\
  3 - Configure simulations & 1 week \\
  4 - Perform simulation and data capture & 8 weeks \\
  Phase 2 \\
  1 - Examination of data & 2 weeks \\
  2 - Data preparation & 4 weeks \\
  3 - Algorithm training & 1 week \\
  4 - Algorithm selection and comparison & 8 weeks \\
  5 - Algorithm tailoring and tuning & 8 weeks \\
  6 - Document final results & * \\
  \midrule
  Thesis submission & & December 4th, 2011 \\
  \bottomrule
\end{tabular}

* Till submission date or completion.

@@

% vim: fdm=syntax wrapmargin=80

>>>>

\input experiment.tex

@@

% vim: fdm=syntax tw=80
